### 2024-10-26 paper/3-motivation.tex
Expand to general control flow

Example 1 is a WebAssembly code example that has a \texttt{loop} whose result
type is \texttt{i32} and has a block of three instructions: \texttt{i32.const},
\texttt{br}, \texttt{unreachable}.
\cref{loop-fig} is the \officialp{} of \texttt{loop} instruction.
It says that the continuation is the start of the loop, the information is
stored in a label, and it \textit{enters} the block with the label.
The term \textit{enter} means that it pushes the label in the stack and makes
pc points to the first instruction in the block.
\texttt{i32.const} instruction is executed first, which just pushes the
\texttt{i32} value \texttt{42} in the stack.
Then, \texttt{br} instruction is executed.
\cref{br-fig} is the \officialp{} of \texttt{br} instruction.
It pops the label from the stack, and makes pc points to the continuation of
the label, which is the start of the loop instruction.
As a result, the code example above is a infinite loop pushing \texttt{42}
forever.

@@

>>>>

Example 1 is a WebAssembly code example that has a \texttt{loop} whose result
type is \texttt{i32} and has a block of three instructions: \texttt{i32.const},
\texttt{br}, \texttt{unreachable}.
\cref{loop-fig} is the \officialp{} of the \texttt{loop} instruction.
It says that the continuation is the start of the loop, the information is
stored in a label, and it \textit{enters} the block with the label.
The term \textit{enter} means that it pushes the label in the stack and makes
pc points to the first instruction in the block.
The \texttt{i32.const} instruction is executed first, which just pushes the
\texttt{i32} value \texttt{42} in the stack.
Then, The \texttt{br} instruction is executed.
\cref{br-fig} is the \officialp{} of the \texttt{br} instruction.
It pops the label from the stack, and makes pc points to the continuation of
the label, which is the start of the loop instruction.
As a result, the code example above is a infinite loop pushing \texttt{42}
forever.

@@

Similar to the control flow using the block and the label, there are many other
control instructions and structures such as a \texttt{call} instruction that
calls a function with a frame and a \texttt{return} instruction that returns from
the function with the frame.
